---
title: "Joerns report"
author: "Joern Grahl"
date: "23-05-2019"
bibliography: literature.bib
output:
  bookdown::html_document2:
    toc: yes
    toc_float: true
    theme: flatly
---

```{r importMyLibraries, include=FALSE}
  # here is place for some code
  # load libraries
  library(tidyverse)
  library(ggplot2)
  library(dplyr)
  library(knitr)
```

# Prologue

# Introduction {#introduction}

```{r plot2, echo=FALSE, fig.cap="Carat against table"}
  ggplot(data=diamonds, aes(x=carat, y=table)) +
    geom_point() +
    theme_bw()
```

## Motivation: why
## Expected results

# Data import

The `diamonds` dataset has `r nrow(diamonds)` observations.

```{r basicInformationDiamonds, echo=FALSE, warning=FALSE}
  # filter, use diamonds of a certain cut
  premium_diamonds <- diamonds %>% 
    filter(cut=="Premium")
```

The `diamonds` dataset has `r nrow(premium_diamonds)` observations.

# Descriptive statistics
## Tables

```{r myTables}
  kable(head(diamonds)) # kableextra
  df <- data.frame(X=1:10, Y=11:20, Z=101:110) # fake data
  summary_stats <- df %>% # start with data frame, and then ...
    summarize_at(
      .vars = c("X", "Y", "Z"), # select variables that should be in the table
      .funs = funs(min, max, mean, median, sd) # which summary statistics do you want?
    ) %>% 
    gather(key, value) %>% # transpose everything, and then ...
    separate(col=key, sep="_", c("feature", "stat")) %>% # make two columns out of var name
    spread(key=stat, value=value) # reapeated obs into multiple columns
  kable(summary_stats)
```

What about factors?

```{r myTableWithAFactor}
  df <- data.frame(X=1:10, Y=11:20, Z=101:110, Cat=c("cat 1", "cat 2")) # fake data
  summary_stats <- df %>% # start with data frame, and then ...
    group_by(Cat) %>% # will do summary stats for each value of Cat seperately
    summarize_at(
      .vars = c("X", "Y", "Z"), # select variables that should be in the table
      .funs = funs(min, max, mean, median, sd) # which summary statistics do you want?
    ) %>% 
    gather(key, value, -Cat) %>% # exclude the category, "transpose", and then ...
    separate(col=key, sep="_", c("feature", "stat")) %>% # make two columns out of var name
    spread(key=stat, value=value) # reapeated obs into multiple columns
  # now you may want to remove the repeated "cat 1" and the repeated "cat 2", and then kable the df.
  kable(summary_stats)
```


## Figures

Figure \@ref(fig:plot) shows carat information against price. 
Figure \@ref(fig:plot2) shows the table information agains price.
Section \@ref(introduction) was the Introduction.


```{r plot, echo=FALSE, fig.cap="Carat against price"}
  ggplot(data=diamonds, aes(x=carat, y=price)) +
    geom_point() +
    theme_bw()
```

The number of observations $n=$ `r nrow(diamonds)`. A simple formular: $\sum_{i=1}^n = 100$.

$$
\begin{equation}
\lim\limits_{x \to \infty \exp(-x)=0}
\end{equation}
$$
The same beast with a number

$$
\begin{equation}
\lim\limits_{x \to \infty \exp(-x)=0}
(#eq:someMath)
\end{equation}
$$
It is trivial to show that \@ref(eq:someMath) is correct.
Previous work (@R-base) has shown that it is wrong.  

# Summary

# Literature 
